Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2020-12-24 inst/manuscript/figures.Rmd
Updates, through placement of risk-metric correlation in SI.

[Check whether the means need to be weighted or not]
[Check whether need to redo median]
```{r segstats, eval=FALSE}
# data("top_label_data")
# data("field_validation_stats")
data("segment_quality_stats")
# data
datnms <- c("top_label_data", "field_validation_stats",
            "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

>>>>

[Check whether the means need to be weighted or not]
[Check whether need to redo median]
```{r segstats, eval=FALSE}
# data("top_label_data")
# data("field_validation_stats")
data("segment_quality_stats")
# data
datnms <- c("top_label_data", "field_validation_stats")#,
            # "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

### 2020-12-24 inst/manuscript/manuscript.Rmd
Updates, through placement of risk-metric correlation in SI.

- name: Sitian Xiong
  affilnum: '1'

- name: Tammy Woodard
  affilnum: '1'

@@

```{r, echo = FALSE, out.width="80%", fig.cap="The overall, user's, and producer's accuracies (indicated by fill color) for each of the 16 mapping zones (zones numbers are shown on maps) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/si_mapping_blocks.png')
```

@@

### Segmentation accuracy
```{r, echo=FALSE}
# validation statistics
data("top_label_data")
data("field_validation_stats")

human <- top_label_data$stats %>%
  mutate(mu_prop = NA, type = "val") %>%
  select(-contains("id"))
machine <- field_validation_stats %>%
  mutate(type = "seg")
humachine <- bind_rows(human, machine) %>% 
  mutate(aoi = as.numeric(gsub("labeller", "", aoi))) %>% 
  arrange(aoi)

huma_aois <- humachine %>% group_by(aoi, type) %>% 
  summarize(med = median(Mean), mu = mean(Mean)) %>% 
  ungroup()
lrgst <- huma_aois %>% select(-med) %>% filter(aoi %in% c(2, 3, 7, 15)) %>% 
  tidyr::pivot_wider(names_from = type, values_from = "mu") %>% 
  filter(seg %in% range(seg))
lrgstlow <- lrgst %>% filter(seg == min(seg))
lrgsthigh <- lrgst %>% filter(seg == max(seg))

# overall stats
huma_sum <- humachine %>% group_by(type) %>% 
  summarize(med = median(Mean), sd = sd(Mean), min = min(Mean), 
            max = max(Mean), mu = mean(Mean)) %>% 
  select(type, mu, med, sd, min, max)
segha <- huma_sum %>% filter(type == "seg") %>% pull(mu) %>% round(2)
valha <- huma_sum %>% filter(type == "val") %>% pull(mu) %>% round(2)
seghamed <- huma_sum %>% filter(type == "seg") %>% pull(med) %>% round(2)
valhamed <- huma_sum %>% filter(type == "val") %>% pull(med) %>% round(2)
seghasd <- huma_sum %>% filter(type == "seg") %>% pull(sd) %>% round(2)
valhasd <- huma_sum %>% filter(type == "val") %>% pull(sd) %>% round(2)

huma_sumn <- humachine %>% group_by(type) %>% 
  summarize(med = median(n), sd = sd(n), min = min(n), max = max(n), 
            mu = mean(n)) %>% 
  select(type, mu, med, sd, min, max)
segn <- huma_sumn %>% filter(type == "seg") %>% pull(mu) %>% round(2)
valn <- huma_sumn %>% filter(type == "val") %>% pull(mu) %>% round(2)
segnmed <- huma_sumn %>% filter(type == "seg") %>% pull(med) %>% round(2)
valnmed <- huma_sumn %>% filter(type == "val") %>% pull(med) %>% round(2)
segnsd <- huma_sumn %>% filter(type == "seg") %>% pull(sd) %>% round(2)
valnsd <- huma_sumn %>% filter(type == "val") %>% pull(sd) %>% round(2)
```
The comparisons of digitized versus segmented field boundaries showed that the mean field size across all 1600 validation sites averaged `r round(segha, 2)` ha (StDev = `r round(seghasd, 2)`), which was `r round((segha - valha) / valha * 100) / 100` times larger than the `r round(valha, 2)` ha (StDev = `r round(valhasd, 2)`) mean area of labeller-digitized polygons. This discrepancy was primarily caused by segmentation results in four AOIs (2, 3, 7, and 15; Figure S5), where segments averaged between `r round(lrgstlow$seg, 2)` and `r round(lrgsthigh$seg, 2)` ha, compared to `r round(lrgstlow$val, 2)` - `r round(lrgsthigh$val, 2)` for the corresponding hand-digitized polygons. In contrast, the median segmented field area was closer to that of digitized polygons (`r seghamed` for segments versus `r valhamed` for labeller polygons). The number of segmented fields per validation site averaged `r segn` (median = `r segnmed`; StDev = `r segnsd`) compared to `r valn` (median = `r valnmed`; StDev = `r valnsd`) for digitized polygons (Figure S6).

### Label quality and map accuracy
```{r, echo = FALSE, out.width="100%", fig.cap="Difference in overall, user's, and producer's accuracy between maps made with consensus labels, the least accurate worker's, and most accurate worker's labels.", fig.align='center', message=FALSE}
knitr::include_graphics('figures/figure6.png')
# library(tidyverse)
# library(cowplot)
# set.seed(1)
# acc_tb <- tibble(aoi = c(1:9, 12, 15), 
#                  Consensus = runif(11, min = 0.75, max = 0.85),
#                  Highest = runif(11, min = 0.72, max = 0.8),
#                  Least = runif(11, min = 0.65, max = 0.75))
# acc_tb <- gather(acc_tb, key = "type", value = "score", -aoi)
# ggplot(acc_tb) + 
#   geom_boxplot(aes(x = type, y = score), fill = "grey") + 
#   xlab("Labelling strategy") + ylab("Accuracy") + 
#   theme(panel.grid.major.y = element_line(colour = "grey80", linetype = 3))
```

@@

- Average field size
- Cropland percentage
- Comparison against other products (croplands.org; Sentinel Landcover)

>>>>

- name: Qi Zhang
  affilnum: '1'

@@

<!-- ```{r, echo = FALSE, out.width="80%", fig.cap="The overall, user's, and producer's accuracies (indicated by fill color) for each of the 16 mapping zones (zones numbers are shown on maps) [This a hypothetical placeholder figure].", fig.align='center'} -->
<!-- knitr::include_graphics('figures/si_mapping_blocks.png') -->
<!-- ``` -->

@@

### Segmentation accuracy
```{r, echo=FALSE}
# validation statistics
data("segment_quality_stats")

datnms <- c("top_label_data", "field_validation_stats")#,
            # "tile_aoi_validation_stats")
for(i in datnms) {
  load(system.file(glue::glue("extdata/{i}.rda"), package = "activemapper"))
}

# extract distributions
human <- top_label_data$stats %>%
  mutate(mu_prop = NA, type = "Validation") %>%
  select(-contains("id"))
machine <- field_validation_stats %>%
  mutate(type = "Segmentation")

# calculate SDs
humac_sds <- bind_rows(
  human %>% summarize(value = sd(Mean)) %>% 
    mutate(type = "v", stat = "sd_ha_mu"), 
  human %>% summarize(value = sd(Median)) %>% 
    mutate(type = "v", stat = "sd_ha_med"), 
  human %>% summarize(value = sd(n)) %>% 
    mutate(type = "v", stat = "sd_n_mu"), 
  machine %>% summarize(value = sd(Mean)) %>% 
    mutate(type = "s", stat = "sd_ha_mu"), 
  machine %>% summarize(value = sd(Median)) %>% 
    mutate(type = "s", stat = "sd_ha_med"), 
  machine %>% summarize(value = sd(n)) %>% 
    mutate(type = "s", stat = "sd_n_mu") 
)

# extract distributions

# human <- top_label_data$stats %>%
#   mutate(mu_prop = NA, type = "val") %>%
#   select(-contains("id"))
# machine <- field_validation_stats %>%
#   mutate(type = "seg")
# humachine <- bind_rows(human, machine) %>% 
#   mutate(aoi = as.numeric(gsub("labeller", "", aoi))) %>% 
#   arrange(aoi)

# huma_aois <- humachine %>% group_by(aoi, type) %>% 
#   summarize(med = median(Mean), mu = mean(Mean)) %>% 
#   ungroup()
# lrgst <- huma_aois %>% select(-med) %>% filter(aoi %in% c(2, 3, 7, 15)) %>% 
#   tidyr::pivot_wider(names_from = type, values_from = "mu") %>% 
#   filter(seg %in% range(seg))
seg_stats_grid <- segment_quality_stats %>% filter(scale == "grid")
lrgst <- seg_stats_grid %>% 
  filter(aoi %in% c(2, 3, 7, 15)) %>% 
  tidyr::pivot_wider(names_from = type, values_from = value) %>%
  filter(Stat == "Mean" & measure == "area")

lrgst_seg <- lrgst %>% summarize(rng = range(Segmentation))
lrgst_val <- lrgst %>% summarize(rng = range(Validation))

# # overall stats
# huma_sum <- humachine %>% group_by(type) %>% 
#   summarize(med = median(Mean), sd = sd(Mean), min = min(Mean), 
#             max = max(Mean), mu = mean(Mean)) %>% 
#   select(type, mu, med, sd, min, max)

segha <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "area") %>% 
  filter(type == "Segmentation" & Stat == "Mean") %>% pull(value) %>% round(2)
# segha <- huma_sum %>% filter(type == "seg") %>% pull(mu) %>% round(2)
valha <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "area") %>% 
  filter(type == "Validation" & Stat == "Mean") %>% pull(value) %>% round(2)
# valha <- huma_sum %>% filter(type == "val") %>% pull(mu) %>% round(2)

# seghamed <- huma_sum %>% filter(type == "seg") %>% pull(med) %>% round(2)
# valhamed <- huma_sum %>% filter(type == "val") %>% pull(med) %>% round(2)
seghamed <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "area") %>% 
  filter(type == "Segmentation" & Stat == "Median") %>% pull(value) %>% round(2)
# segha <- huma_sum %>% filter(type == "seg") %>% pull(mu) %>% round(2)
valhamed <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "area") %>% 
  filter(type == "Validation" & Stat == "Median") %>% pull(value) %>% round(2)

# seghasd <- huma_sum %>% filter(type == "seg") %>% pull(sd) %>% round(2)
seghasd <- humac_sds %>% filter(type == "s" & stat == "sd_ha_mu") %>% 
  pull(value) %>% round(2)
# valhasd <- huma_sum %>% filter(type == "val") %>% pull(sd) %>% round(2)
valhasd <- humac_sds %>% filter(type == "v" & stat == "sd_ha_mu") %>% 
  pull(value) %>% round(2)

segnsd <- humac_sds %>% filter(type == "s" & stat == "sd_n_mu") %>% 
  pull(value) %>% round(2)
valnsd <- humac_sds %>% filter(type == "v" & stat == "sd_n_mu") %>% 
  pull(value) %>% round(2)

# huma_sumn <- humachine %>% group_by(type) %>% 
#   summarize(med = median(n), sd = sd(n), min = min(n), max = max(n), 
#             mu = mean(n)) %>% 
#   select(type, mu, med, sd, min, max)
# segn <- huma_sumn %>% filter(type == "seg") %>% pull(mu) %>% round(2)
# valn <- huma_sumn %>% filter(type == "val") %>% pull(mu) %>% round(2)
# segnmed <- huma_sumn %>% filter(type == "seg") %>% pull(med) %>% round(2)
# valnmed <- huma_sumn %>% filter(type == "val") %>% pull(med) %>% round(2)
# segnsd <- huma_sumn %>% filter(type == "seg") %>% pull(sd) %>% round(2)
# valnsd <- huma_sumn %>% filter(type == "val") %>% pull(sd) %>% round(2)

segn <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "n") %>% 
  filter(type == "Segmentation" & Stat == "Mean") %>% pull(value) %>% round(2)
valn <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "n") %>% 
  filter(type == "Validation" & Stat == "Mean") %>% pull(value) %>% round(2)

segnmed <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "n") %>% 
  filter(type == "Segmentation" & Stat == "Median") %>% pull(value) %>% round(2)
valnmed <- seg_stats_grid %>% 
  filter(aoi == "All" & measure == "n") %>% 
  filter(type == "Validation" & Stat == "Median") %>% pull(value) %>% round(2)

```
The comparisons of digitized versus segmented field boundaries showed that the mean field size across all 1600 validation sites averaged `r round(segha, 2)` ha (Median = `r round(seghamed, 2)`; StDev = `r round(seghasd, 2)`), which was `r round((segha - valha) / valha * 100) / 100` times larger than the `r round(valha, 2)` ha (Median = `r round(valhamed, 2)`; StDev = `r round(valhasd, 2)`) mean area of labeller-digitized polygons. This discrepancy was primarily caused by segmentation results in four AOIs (2, 3, 7, and 15; Figure S5), where segments averaged between `r round(lrgst_seg$rng[1], 2)` and `r round(lrgst_seg$rng[2], 2)` ha, compared to `r round(lrgst_val$rng[1], 2)` - `r round(lrgst_val$rng[2], 2)` ha for the corresponding hand-digitized polygons. The number of segmented fields per validation site averaged `r segn` (median = `r segnmed`; StDev = `r segnsd`) compared to `r valn` (median = `r valnmed`; StDev = `r valnsd`) for digitized polygons (Figure S6).

<!-- ### Label quality and map accuracy -->
<!-- ```{r, echo = FALSE, out.width="100%", fig.cap="Difference in overall, user's, and producer's accuracy between maps made with consensus labels, the least accurate worker's, and most accurate worker's labels.", fig.align='center', message=FALSE} -->
<!-- knitr::include_graphics('figures/figure6.png') -->
<!-- # library(tidyverse) -->
<!-- # library(cowplot) -->
<!-- # set.seed(1) -->
<!-- # acc_tb <- tibble(aoi = c(1:9, 12, 15),  -->
<!-- #                  Consensus = runif(11, min = 0.75, max = 0.85), -->
<!-- #                  Highest = runif(11, min = 0.72, max = 0.8), -->
<!-- #                  Least = runif(11, min = 0.65, max = 0.75)) -->
<!-- # acc_tb <- gather(acc_tb, key = "type", value = "score", -aoi) -->
<!-- # ggplot(acc_tb) +  -->
<!-- #   geom_boxplot(aes(x = type, y = score), fill = "grey") +  -->
<!-- #   xlab("Labelling strategy") + ylab("Accuracy") +  -->
<!-- #   theme(panel.grid.major.y = element_line(colour = "grey80", linetype = 3)) -->
<!-- ``` -->

@@

Map figure:
- Panel A: Cropland probability map (0.005 degree resolution)
  - Panel A insets: Probability close-ups in AOIs 1, 8, 13, 15
- Panel B: Cropland percentage map (0.005 degree)
  - Panel B insets: Segment close-ups in AOIs 1, 8, 13, 15
- Panel C: Median field size
- Panel D: Field number
- Median field size
- Cropland percentage

Stats figure: 
- Mean field size per AOI
- Median field size per AOI
- SD fields per AOI 
- N field per AOI

### 2020-12-24 inst/manuscript/si.Rmd
Updates, through placement of risk-metric correlation in SI.

\clearpage
# Results
## Image quality
```{r, echo=FALSE}
data("image_quality")
wqual_diff <- image_quality$img %>% filter(kml_type == "F") %>%
  group_by(name, season, worker_id) %>%
  summarize(tile = min(tile), score = sum(score) / 12) %>% 
  ungroup() %>% 
  pivot_wider(names_from = worker_id, values_from = score,
              names_prefix = "w") %>%
  select(tile, season, w92, w99) %>% 
  mutate(d = w92 - w99, 
         absd = abs(d))
```

@@

@@

### Field area and number
To mean, median, and distributions of the average area of segmented field boundaries over the 100 validation sites in each AOI are compared to the areas of the polygons digitized by the most accurate labeller over the same sites in Figure \ref{fig:areavalidation}. The same statistics for average number of segments versus average number of labelled polygons across validation sites in each AOI are shown in Figure \ref{fig:numbervalidation}.      
```{r areavalidation, echo = FALSE, out.width="100%", fig.cap="The distributions of the average areas (in hectares) of segmented field boundaries (shown in blue) at the 100 validation sites per AOI, compared with the average areas of field boundaries digitized (shown in red) by the most accurate worker to label each site. Vertical lines indicate the mean and median of each distribution.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_validation_stats_fha.png')
```

```{r numbervalidation, echo = FALSE, out.width="100%", fig.cap="The distributions of the average number of segmented field boundaries (shown in blue) at the 100 validation sites per AOI, compared with the average number of digitized polygons (shown in red) by the most accurate worker to label each site. The mean and median of each distribution is shown. Vertical lines indicate the mean and median of each distribution.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_validation_stats_fn.png')
```

>>>>

\clearpage
# Results
## Image quality
```{r, echo=FALSE, message=FALSE, warning=FALSE}
data("image_quality")
wqual_diff <- image_quality$img %>% filter(kml_type == "F") %>%
  group_by(name, season, worker_id) %>%
  summarize(tile = min(tile), score = sum(score) / 12) %>% 
  ungroup() %>% 
  pivot_wider(names_from = worker_id, values_from = score,
              names_prefix = "w") %>%
  select(tile, season, w92, w99) %>% 
  mutate(d = w92 - w99, 
         absd = abs(d))
```

@@

The association between the average label risk per AOI and several model performance metrics, assessed using Spearman Rank Correlation, is shown in Table \ref{tab:labelrisk_v_metrics}.

```{r labelrisk_v_metrics, echo=FALSE}
data("label_risk")
data("iteration_metrics")

risk <- label_risk$stats %>% 
  filter(usage == "Train") %>% 
  filter(aoi %in% 1:16) %>% 
  select(-usage)

mets <- c("Accuracy", "AUC", "F1", "TSS", "Precision", "Recall", "FPR")
metrics <- iteration_metrics %>% 
  filter(Metric %in% mets) %>% 
  mutate(AOI = as.factor(gsub("labeller", "", AOI))) %>% 
  filter(AOI %in% 1:16) %>% 
  # pivot_wider(names_from = Metric, values_from = Score) %>% 
  group_by(AOI) %>% filter(Iteration == max(Iteration)) %>% 
  select(-Iteration)

risk_metrics <- left_join(risk, metrics, by = c("aoi" = "AOI"))

cor_fun <- function(df) {
  cor.test(df$Risk, df$Score, method = "spearman") %>% broom::tidy()
}

risk_corr <- lapply(unique(risk_metrics$Metric), function(x) {
  dat <- risk_metrics %>% filter(Metric == x)
  cor_fun(dat) %>% mutate(Metric = x)
}) %>% do.call(rbind, .) %>% 
  select(estimate, Metric) %>% 
  rename(r = estimate)
nms <- risk_corr$Metric
risk_corr <- round(t(risk_corr[, 1]), 3)
colnames(risk_corr) <- nms

cap <- glue::glue("Spearman's Rank correlation between the average label risk per AOI and a variety of model performance metrics.")
kable(risk_corr, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) #%>% 
  # column_spec(1, width = "8cm")
```

@@

### Field area and number
To mean, median, and distributions of the average area of segmented field boundaries over the 100 validation sites in each AOI are compared to the areas of the polygons digitized by the most accurate labeller over the same sites in Figure \ref{fig:areavalidation}. The same statistics for average number of segments versus average number of labelled polygons across validation sites in each AOI are shown in Figure \ref{fig:numbervalidation}.      
```{r areavalidation, echo = FALSE, out.width="100%", fig.cap="The distributions of the average areas (in hectares) of segmented field boundaries (shown in blue) at the 100 validation sites per AOI, compared with the average areas of field boundaries digitized (shown in red) by the most accurate worker to label each site. Vertical lines indicate the mean and median of each distribution.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_validation_stats_fha2.png')
```

```{r numbervalidation, echo = FALSE, out.width="100%", fig.cap="The distributions of the average number of segmented field boundaries (shown in blue) at the 100 validation sites per AOI, compared with the average number of digitized polygons (shown in red) by the most accurate worker to label each site. The mean and median of each distribution is shown. Vertical lines indicate the mean and median of each distribution.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_validation_stats_fn2.png')
```
